Interpreting Random Forest Predictions for Bullet Matching Using LIME (?)

### 2018-09-24 paper/paper.Rmd
updated paper structure

---
title: "Interpreting Random Forest Predictions for Bullet Matching Using LIME (?)"
author: "Katherine Goode and Heike Hofmann"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Background/Literature Review

# Problem Statement

# Overview of LIME

# The Hamby 224 Clone

@@

# Applying LIME

```{r}
# Read in the Hamby 224 combined test data and explanations
hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")

hamby224_test_explain %>% 
  filter(set == "1") %>% 
  select(case, bullet1:land2, rfscore) %>%
  distinct() %>%
  ggplot(aes(x = land1, y = land2)) + 
  geom_tile(aes(fill = rfscore)) +
  facet_grid(bullet1 ~ bullet2) +
  theme_bw() + 
  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5)

@@

# Results (using LIME on a TS)

>>>>

---
title: "Interpreting Random Forest Predictions for Bullet Matching Using LIME (?)"
author: "Katherine Goode and Heike Hofmann"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  pdf_document:
    number_sections: true
bibliography: references.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)

# Load libraries
library(dplyr)
library(ggplot2)
```

# Introduction

- background
- motivation
- literature review
- problem statement

# Data

## Training Data: The Hamby...

## Testing Data: The Hamby 224 Clone

@@

#  Methods

## Random Forest Model

## Overview of LIME

## Applying LIME

## Visualizing the LIME Explanations

```{r}
# Read in the Hamby 224 combined test data and explanations
hamby224_test_explain <- readRDS("../data/hamby224_test_explain.rds")
```

```{r}
hamby224_test_explain %>%
  filter(set == "1") %>%
  select(case, bullet1:land2, rfscore) %>%
  distinct() %>%
  ggplot(aes(x = land1, y = land2)) +
  geom_tile(aes(fill = rfscore)) +
  facet_grid(bullet1 ~ bullet2) +
  theme_bw() +
  scale_fill_gradient2(low = "grey", high = "orange", midpoint = 0.5)

@@

# Results

# Discussion
